% !TeX root = exercise02.tex
\input{common/header}
\begin{document}
\newcommand{\dozenten}{Prof.~Dr.~Steffen Herbold}
\newcommand{\vorlesung}{Principles of AI Engineering}
\newcommand{\docauthor}{Lukas Schulte}
\newcommand{\semester}{}
\newcommand{\blattnummer}{2}
\newcommand{\bistermin}{}
\input{common/logo}


\section*{Project task}
% Analyzing the data and pre-processing

Your coworker provided a first dataset, which you can use to train your AI model (\texttt{sample1.csv.gz} in StudIP). Load the data into a Jupyter Notebook, inspect it and implement appropriate text pre-processing steps. Collect at least one example which shows what each of your pre-processing steps does.

\vspace{5px}

Hint:
Next week's exercise will deal with creating the model. The model (a random forest model) will be built with \href{https://scikit-learn.org}{sklearn}\footnote{\url{https://scikit-learn.org}}.

\section*{Questions}

\begin{enumerate}
      \item
            Analyze the dataset.
            \begin{itemize}
                  \item Which fields are relevant for the prediction in the given project scenario?
                  \item Is the dataset even suitable for the task at hand? Do you spot potential problems?
            \end{itemize}
      \item
            Define the following text pre-processing steps:
            \begin{itemize}
                  \item Tokenization
                  \item Normalization
                  \item Noise removal
                  \item Stemming
                  \item Lemmatization
                  \item Stop-word removal
            \end{itemize}
      \item
            Explain concept drift and how it would impact your application.
            Describe how you would mitigate the effects.
      \item
            Describe what could be considered a feedback loop in your application and why that can be a problem.
            Explain how you can measure the effect.
\end{enumerate}

\end{document}
