% !TeX root = exercise09.tex
\input{common/header}
\begin{document}
\newcommand{\dozenten}{Prof.~Dr.~Steffen Herbold}
\newcommand{\vorlesung}{Principles of AI Engineering}
\newcommand{\docauthor}{Lukas Schulte}
\newcommand{\semester}{}
\newcommand{\blattnummer}{9}
\newcommand{\bistermin}{}
\input{common/logo}


\section*{Project task}
% Metrics endpoint and monitoring

Prometheus and Grafana are commonly used to monitor metrics of various kinds. Implement a metrics endpoint using the Prometheus client for Python.\footnote{\url{https://github.com/prometheus/client_python}} Add at least the following metrics:

\begin{itemize}
      \item Accuracy (updated after every correction)
      \item Average prediction confidence
      \item Number of predictions per category
      \item Number of correct predictions per category
      \item Number of incorrect predictions per category
\end{itemize}

A tutorial to get started with the Prometheus client in Python is available in the official \href{https://prometheus.github.io/client_python/}{documentation}\footnote{\url{https://prometheus.github.io/client_python/}}.

\vspace{5px}

Monitoring the data produced by the metrics endpoint requires the setup of a Prometheus server and a Grafana instance. One way to create such a setup is docker-compose. You can find a reference for such a setup \href{https://git.fim.uni-passau.de/aie/excercises/principles-of-ai-engineering/monitoring-setup}{here}\footnote{\url{https://git.fim.uni-passau.de/aie/excercises/principles-of-ai-engineering/monitoring-setup}}. If you cannot run docker due to hardware limitations, contact the TA as soon as possible.

\section*{Questions}

\begin{enumerate}
      \item
            Describe how you would design human oversight for the described system, consider the consequences of mistakes, possibilities of reviewing model decisions and telemetry.
      \item
            Given the problem description, describe what could be a non-ML alternative to solve the problem.
            Describe what would change in the system if it would be solved without machine learning.
\end{enumerate}

\end{document}
